---
title: "Build Dataset"
author: "Timothy Fraser"
date: "July 12, 2021"
output: html_notebook
---

# 0. Packages

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(readr)
```

# 1. Census Data

Let's import raw census data, compile it, and export it.

```{r,  warning = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
bind_rows(
  
  # Import a select few variables from this dataset
  read_csv("estat_data_part_a.csv", skip = 8) %>%
    mutate_all(funs(as.double(str_remove_all(., "[,]")))),
  
  read_csv("estat_data_part_a2.csv", skip = 8) %>%
    mutate_all(funs(as.double(str_remove_all(., "[,]"))))
  ) %>%
  # Recode area code
  mutate(muni_code = `AREA Code` %>% str_pad(5, "left", "0")) %>%

  # Join in other data
  left_join(by = c("muni_code", "YEAR"),
            y = bind_rows(
              
              read_csv("estat_data_part_b.csv", skip = 8) %>%
                mutate_all(funs(as.double(str_remove_all(., "[,]")))),
              
              read_csv("estat_data_part_b2.csv", skip = 8) %>%
                mutate_all(funs(as.double(str_remove_all(., "[,]"))))
              ) %>%
              # Recode area code
              mutate(muni_code = `AREA Code` %>% str_pad(5, "left", "0"))
            ) %>%
  # Select and rename data
  select(muni_code,
         year = YEAR,
         pop = "A1101_Total population (Both sexes)[person]",
         exp_fire = "D320309_(Expenditure) Fire service (local public finance, municipalities)[thousand yen]",
         exp_dis_relief = "D320311_Disaster relief expenditure (municipalities)[thousand yen]",
         kindergartens =  "E1101_Number of kindergartens[number of kindergartens]",
         elementary = "E2101_Number of elementary schools[number of schools]",
         secondary = "E3101_Number of lower secondary schools[number of schools]",
         upper_secondary = "E4101_Number of upper secondary schools[number of schools]",
         public_halls = "G1201_No. of public halls[number of community centers]",
         libraries = "G1401_No. of libraries[number of community centers]",
         owned_homes = "H1310_No. of owned houses[dwellings]",
         rented_homes = "H1320_No. of rented houses[dwellings]",
         public_rented_homes = "H1321_No. of rented houses owned by local government, urban renaissance agency or public corporation[dwellings]",
         rented_homes_public_govt = "H132101_No. of rented houses owned by local government[dwellings]",
         rented_homes_public_not_govt = "H132102_No. of rented houses owned by urban renaissance agency or public corporation[dwellings]",
         rented_homes_private = "H1322_No. of rented houses owned privately[dwellings]",
         owned_homes_earthquake_resist_built = "H2270_No. of dwellings getting earthquake resistance construction (Owned)[dwellings]",                                                                   
         owned_homes_earthquake_resist_renov = "H227004_Total No. of owned houses renovated to make it earthquake-resistant in and after 2009[dwellings]",
         # Population density
         pop_density = "#A01202_Population per 1 km2 of inhabitable area[person]",
         income_thous = "C120110_Taxable income[thousand yen]",
         employee_secondary = "C2204_Number of persons engaged (secondary industry) (Establishments and Enterprise Census)[person]",
         employee_tertiary = "C2205_Number of persons engaged (tertiary industry) (Establishments and Enterprise Census)[person]",
         unemployment = "#F01301_Unemployment rate (both sexes)[%]",
         inmigrants = "A5101_Number of in-migrants from other municipalities[person]",
         outmigrants = "A5102_Number of out-migrants to other municipalities[person]",
         pop_over_age_65 = "A1303_Total population (65 and over)[person]",
         pop_women = "A110102_Total population (Female)[person]",
         land_price_residential = "C5401_Average price for land transaction (Residential quarter)[yen/m2]",
         exp_social_assistance = "D320404_(Expenditure) Social assistance (local public finance, municipalities)[thousand yen]") %>%
  
  # Join in a few additional variables
  left_join(
     # Join using municipality code and year
    by = c("muni_code", "year"),
    y = read_csv("more_stats.csv") %>%
      # repair 5-digit municipality code
      mutate(muni_code = muni_code %>% str_pad(5,"left","0")) %>%
      # select main variables
      select(year, muni_code,
             financial_strength_index = financial_strength_index_2016,
             rev_to_exp_ratio = rev_to_exp_ratio_2016,
             exp_public_works = exp_public_works_thous_2016) %>%
      # Convert to numeric
      mutate_at(vars(financial_strength_index, rev_to_exp_ratio), 
                funs(as.numeric)) %>%
      mutate(exp_public_works = exp_public_works %>% str_remove_all("[,]") %>% parse_number()) 
    ) %>%
  
  
  
  # Pivot to long form
  pivot_longer(cols = -c(muni_code, year),
               names_to = "measure",
               values_to = "value") %>%
  
  # Remove urban wards outside of Tokyo from data
  filter(muni_code %in% read_csv("muni_code.csv")$muni_code) %>%
  
  # Export to file
  write_csv("dataset_processing.csv")

```


Next, we identify which of the variables we collected are missing less than 5% of data points in any year after 2010. Those which meet our criteria are eligible variables we can use for our analysis.

```{r,  warning = FALSE, message = FALSE, warning = FALSE}
# Identify variables missing less than 5% of data for a year
read_csv("dataset_processing.csv") %>%
  group_by(measure, year) %>%
  # Count missing data, divided by total
  summarize(
    missing = sum(
      if_else(is.na(value), 1, 0)) / n()) %>%
  # Filter to just those missing less than 5%
  # and those pertaining to years during or after 2000
  filter(missing < 0.05 & year >= 2000) %>% ungroup %>%
  # Create variable name with year
  mutate(measure = paste(measure, year, sep = "_")) %>%
  select(measure)
```


Next, we want to create a smaller dataset of our eligible variables, merging our variables from the social capital index into the list of 1741 municipalities.

```{r,  warning = FALSE, message = FALSE, warning = FALSE}

# Import new social capital indices
index <- read_csv("indices_V2_2020_10_28.csv") %>%
  select(muni_code, year, social_capital, bonding, bridging, linking, vulnerability)

# Now bind everything together
read_csv("muni_code.csv") %>% 
  # Extract prefecture names and codes
    mutate(pref = word(muni_en, 1),
         pref_code = str_sub(muni_code, 1,2)) %>%
  left_join(by = "muni_code",
            # Import in valid variables
            y = read_csv("dataset_processing.csv") %>%
              pivot_wider(id_cols = c(muni_code, year),
                          names_from = measure,
                          values_from = value) %>%
              # Get most recent variables that were valid
              select(year, muni_code, pop,
                     kindergartens, elementary, 
                     secondary, upper_secondary,
                     public_halls, libraries, 
                     exp_fire, exp_dis_relief,
                     exp_public_works, # rename
                     exp_social_assistance,
                     financial_strength_index,
                     rev_to_exp_ratio,
                     
                     pop_over_age_65,
                     pop_women,
                     unemployment,
                     pop_density,
                     inmigrants,
                     outmigrants,
                     income_thous)) %>%
  # Arrange
  arrange(muni_code, desc(year)) %>%
  # Fill in missing cases where able using previous values or most recent values
  group_by(muni_code) %>%
  fill(pop:income_thous, .direction = "downup") %>%
  # Now for each row, calculate the following:
              rowwise() %>%
              mutate(
                # count total number of potential public shelters per thousand persons
                shelters_per_capita = sum(
                  kindergartens, elementary, secondary, 
                  upper_secondary, public_halls, libraries) / pop * 1000,
                # Get spending on emergencies, disasters, and public works per capita (in thousands of yen)
                exp_fire_per_capita = exp_fire / pop,
                exp_dis_relief_per_capita = exp_dis_relief / pop,
                exp_public_works_per_capita = exp_public_works / pop,
                exp_social_assistance_per_capita = exp_social_assistance / pop,
                income_thous_per_capita = income_thous / pop,
                
                pop_women = pop_women / pop * 100,
                pop_over_age_65 = pop_over_age_65 / pop * 100,
                total_migration = (inmigrants + outmigrants) / pop * 1000,
                net_migration = (inmigrants - outmigrants) / pop * 1000) %>%
  
  # We have created three more of our main control variables:
  # emergency services spending (proxy: expenditure of fire departments)
  # shelters per capita (proxy: schools and community centers)
  # population
  # Join in disaster data
  left_join(by = "muni_code",
            y = readxl::read_excel("Database_prefectural_analysis_R.xlsx") %>% 
              select(muni_code = Code, death11, destroy11, damaged11, coast)  %>%
              # Creat fukushima exclusion zone
              mutate(fukushima = if_else(muni_code %in% c("07211", # tamura-shi
                                                          "07212", # minamisoma-shi
                                                          "07546", # futaba
                                                          "07564", # iitate
                                                          "07548", # katsurao
                                                          "07308", # kawamata
                                                          "07544", # kawauchi
                                                          "07545", # okuma
                                                          "07547", # namie
                                                          "07542", # naraha
                                                          "07543"), # tomioka
                                         true = 1, false = 0))) %>%
  mutate(damage_rate = (destroy11 + damaged11) / pop * 1000,
         death_rate = death11 / pop * 1000) %>%
  mutate_at(vars(death_rate, damage_rate), funs(if_else(is.na(.), 0, false = .))) %>%
  mutate_at(vars(death11, destroy11, damaged11, coast,
                 fukushima, death_rate, damage_rate),
            funs(if_else(year <= 2010, true = 0, false = .))) %>%
  
  # Join in vulnerability and social capital data
  left_join(
    by = c("year", "muni_code"),
    y = index) %>%
  # Fix any infinites (created by dividing by population in a town with zero residents; this should be classified as missing)
    mutate_at(vars(pop:vulnerability),
            funs(if_else(is.infinite(.) | is.nan(.), true = NA_real_, false = .))) %>%
  # Export these to file
  arrange(muni_code, desc(year)) %>%
  filter(year %in% c(2000:2017)) %>%
  write_csv("dataset.csv")
  
```

